Bird beak's elaboration and exploration

### 2021-05-28 Analysis/03-elaboration_exploration_analyses.Rmd
Update 03-elaboration_exploration_analyses.Rmd

>>>>

Following the ways to:
 1. estimate the variance-covariance matrices of the phylogenetic effects in trait space (02-MCMCglmm_mini_chains.Rmd);
 2. extracting the major axes of variation of these VCV matrices for the different levels in the phylogeny;
 3. and calculating the elaboration and exploration scores for elements in the trait space based on these major axes;

We can measure these scores for each clade and each species separately.

## Elaboration and exploration by clade

To run the analyses per clade we compared the major axes for each clade to the major axes for the overall phylogenetic effect (e.g. plovers' VCV vs. all birds' VCV, etc.).

To do so, for randomly selected posterior variance-covariance matrix we defined $\vec{a}$ as the major axes for the clade of interest and projected it onto $\vec{B}$ as the major overall phylogenetic effect (see above).
For each pair of $\vec{a}$ and $\vec{B}$, we translated the origin of $\vec{a}$ onto the origin of $\vec{B}$ and measured the projection (elaboration), rejection (exploration) and angle (degree of exploration).

```{r}
## Get all the angles and stuff
group_results <- analyses.group(major_axes[1:4], base = "animal")
names(group_results) <- levels(demo_data$clade)
```

The results are reported as boxplots of **log values** for each group indicating which group explores/elaborates more (and to which degree - angle) relatively to each other.

```{r, fig.height = 18, fig.heigh = 6}
## Plot the blob wise metrics
plot.analyses.group(lapply(group_results, log), col = colour_vector)
```

## Elaboration and exploration by species

Similarly to the analyses described above, we ran the analyses per species but here we directly compared each species position in the space to the same vector $\vec{B}$ described above and reported the results per groups.

```{r}
## Global analyses
tip_results_global <- analyses.tip(data = demo_data[, c(1:4)], axes = major_axes$animal)
```

And here are the **log values** plotted by group:

```{r}
## Plot results
plot.analyses.tip(lapply(tip_results_global, log), col = colour_vector, group = split(rownames(demo_data), f = demo_data$clade))
```

Note that here only the tips positions projected on the global phylogenetic axes.

We also looked at the exploration elaboration profiles within each clades by replacing for each clade, the projection of the elements onto $\vec{B}$ to the projection onto their respective clade major axes $\vec{a}$.

TODO!
